---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(studentenstatistikNRW)
```

# studentenstatistikNRW

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/studentenstatistikNRW)](https://CRAN.R-project.org/package=studentenstatistikNRW)
<!-- badges: end -->

## Overview

This package contains all student statistics tables ("21311 Statistik der Studenten") of the Landesdatenbank NRW. The data is obtained using the [wiesbaden package](https://github.com/sumtxt/wiesbaden) by Moritz Marbach. 

## Installation

And the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("RichardMeyer-Eppler/studentenstatistikNRW")
```

## Data

This package provides the following tables:

```{r, echo = FALSE}
knitr::kable(
  studentenstatistikNRW::df_table %>% 
  dplyr::mutate(
    tablename = paste0(
      "`?df_",
      tablename,
      "`"
    )
  )
)
```

## Data license for the Destatis data

Data obtained from Destatis is available under the [Data licence Germany –
attribution – version 2.0 (dl-de/by-2-0)](www.govdata.de/dl-de/by-2-0). The data
in this package was obtained from the Landesdatenbank NRW using the code 
"21311" for "Statistik der Studenten". The license requests a reference to the 
dataset using the URI. To the best of my knowledge, the Landesdatenbank NRW does
not yet provide Uniform Resource Identifiers (URI) to identify these tables.
