---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(studentenstatistikNRW)
```

# studentenstatistikNRW

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/studentenstatistikNRW)](https://CRAN.R-project.org/package=studentenstatistikNRW)
<!-- badges: end -->

## Overview

This package contains all student statistics tables ("21311 Statistik der Studenten") of the [Landesdatenbank NRW](https://www.landesdatenbank.nrw.de/). The package is created by downloading the data using the [wiesbaden package](https://github.com/sumtxt/wiesbaden) by Moritz Marbach. 

## Installation

The package is not yet on CRAN. Install the development version from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# Package remotes needs to be installed!
# install.packages("remotes")
remotes::install_github("RichardMeyer-Eppler/studentenstatistikNRW")
```

## Data

The table below lists all tables included by the package. They are all part of the student statistics tables ("21311 Statistik der Studenten") of the [Landesdatenbank NRW](https://www.landesdatenbank.nrw.de/):

```{r, echo = FALSE}
knitr::kable(
  studentenstatistikNRW::tables |> 
  dplyr::mutate(
    tablename = paste0(
      "`?df_",
      tablename,
      "`"
    )
  )
)
```

## Data manipulation

The downloaded raw data cannot be included in this package, as it has a size of roughly 200 MB. The licence requires a list of all changes as part of the source notes (see below). These are the data transformation steps performed:

* Column names are transformed using `janitor::clean_names()`.
* Technical columns ending in "QUAL", "ERR", or "LOCK" are removed.
* The original data uses value labels with separate lookup tables. For the R package, these labels are transformed into factors using the description from the lookup tables.

## License for the data from the Landesdatenbank NRW / Destatis

The data in this package was obtained from the [Landesdatenbank NRW](https://www.landesdatenbank.nrw.de/) using the code "21311" for "Statistik der Studenten". The licence for data obtained from the Landesdatenbank NRW / Destatis is available here (see paragraph 2 section 2): [Data licence Germany – attribution – Version 2.0](http://www.govdata.de/dl-de/by-2-0). Paragraph 2 section 3 requires including a reference to the dataset (URI) if available. To the best of my knowledge, the Landesdatenbank NRW does not yet provide Uniform Resource Identifiers (URI) to identify their tables.

Paragraph 3 stipulates that "changes, editing, new designs or other amendments must be marked as such in the source note". Compared to the raw data, the following changes were made: (1) column names were changed to lower case, (2) some technical columns were excluded and (3) value labels were turned into factors using the description of each value label. The code for all these transformations is available through this package.
