---
title: "Using labelled data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using labelled data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(studentenstatistikNRW)
library(labelled)
library(gtsummary)
```

# Resources on Using the Labelled Package
* [Joseph Larmarange - Labelled Package](https://larmarange.github.io/labelled/index.html)
* [Daniel D. Sjoberg - gtsummary Package](https://www.danieldsjoberg.com/gtsummary/)
* [Shannon Pileggi - Leveraging labelled data in R](https://www.pipinghotdata.com/posts/2020-12-23-leveraging-labelled-data-in-r/)
* [Shannon Pileggi - Polished summary tables in R with gtsummary](https://www.pipinghotdata.com/posts/2021-07-14-polished-summary-tables-in-r-with-gtsummary/)
* [Shannon Pileggi - The case for variable labels in R](https://www.pipinghotdata.com/posts/2022-09-13-the-case-for-variable-labels-in-r/)

# Example data frame

Select a random table in `studententstatistikNRW::tables`:

```{r df}
# https://stackoverflow.com/questions/9057006/getting-strings-recognized-as-variable-names-in-r
df <- get(
  get_table_name(
    tables |> 
      dplyr::slice_sample(n = 1) |> 
      dplyr::pull(tablename)
  )
) 

df
```

# Variable labels

Show variable labels with `labelled::var_label` for all variables:

```{r var-label}

labelled::var_label(
  x = df
)

```

# Look for

`labelled::look_for` is meant to help users finding variables in large datasets:

```{r look-for}
# All variables
labelled::look_for(
  df
)

# All variables starting with "BIL"
labelled::look_for(
  df,
  "BIL"
)

```

For more details:

```{r look-for-details}
# Default printing
labelled::look_for(
  df,
  details = "full"
)

# Tibble
labelled::look_for(
  df,
  details = "full"
) |> 
  tibble::as_tibble()

# List columns as character
labelled::look_for(
  df,
  details = "full"
) |> 
  labelled::convert_list_columns_to_character()
```

# Factors

Use `labelled::to_factor` for easy factor conversion:

```{r to-factor}
df_factor <- df |>  
  labelled::to_factor(
    levels = "labels",
    ordered = TRUE,
    sort_levels = "labels",
    strict = FALSE, # Convert to factor only if all values have a defined label?
    labelled_only = TRUE # for a data.frame, convert only labelled variables to factors?
  )

df_factor
```

# GT Summary

```{r gt-summary}

df_factor |> 
  gtsummary::tbl_summary()

```

